%! Author = Alexander Hinze
%! Date = 08.11.22

\wordingbox{CPU}{
    The central processing unit, or CPU for short is the main processor
    of the computer and responsible for coordinating all other hardware.
}

\wordingbox{GPU}{
    The graphics processing unit, or GPU for short is a secondary processor
    usually found in modern computers, which is responsible for performing
    vectorized arithmetic operations (SIMD) as well as outputting a picture
    to the screen(s).
}

\wordingbox{ALU}{
    The arithmetic logic unit, or ALU is a part of the circuitry inside
    the CPU which is responsible for performing basic arithmetic operations,
    like addition, subtraction, multiplication and division.
}

\wordingbox{AST}{
    An abstract syntax tree is a tree representation of
    the abstract syntactic structure of text (often source code)
    written in a formal language.
    Each node of the tree denotes a construct occurring in the text.
}

\wordingbox{UDT}{
    A UDT, or user-defined-type is a non-builtin type,
    which may provide function prototypes, implement them
    or define member variables (fields).
}

\wordingbox{Value Type}{
    A value type is a type which is always passed by value
    instead of by reference by default without exceptions.
}

\wordingbox{Managed Type}{
    A managed type is a type which is either (atomically)
    reference counted or even garbage collected depending
    on the target platform.
}

\wordingbox{Token Stream}{
    A token stream is an intermediary state of the source
    code before it is turned into an AST right after lexing.
    The text is split into a list of categorized symbols called
    tokens, which can be modified during the compilation process.
}